A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-19 manuscript.Rmd
add webshots to docker: - install google chrome in docker - install webshot2

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
csl: apa7.csl
numbered_headings: true
toc_depth: 5
bibliography: references.bib
---
